Title

### 2013-02-05 inc/photocathode/plasmon/plasmon.tex
some bugfixes

Collaborators at Argonne National Laboratory's Electron Microscopy Center, Material Science Division employed a defocused Gallium focused ion beam (FIB) (Zeiss 1540XB) to iteratively mill an approximately sinusoidal shape into the surface of a silicon wafer.
Several regions were created each 100x100$\mu$m in area, having a $\sim$1$\mu$m period and $\sim$10\% modulation depth.
Given a laser wavelength of 523nm ($\varepsilon_{Au} \approx –3.95$ \cite{johnson_optical_1972}), this choice of periodicity corresponds by \ref{eq:plasmon_condition} to an incidence angle of $\sim39^{\circ}$, which is within the acceptance range of our experimental setup (35-75$^{\circ}$). %TODO point to Togawa section
An SEM image of one such region is shown in \ref{fig:fib-si-sem}.

>>>>

Collaborators at Argonne National Laboratory's Electron Microscopy Center, Material Science Division employed a defocused Gallium focused ion beam (FIB) (Zeiss 1540XB) to iteratively mill an approximately sinusoidal shape into the surface of a silicon wafer.
Several regions were created each 100x100$\mu$m in area, having a $\sim$1$\mu$m period and $\sim$10\% modulation depth.
Given a laser wavelength of 523nm ($\varepsilon_{Au} \approx -3.95$ \cite{johnson_optical_1972}), this choice of periodicity corresponds by \ref{eq:plasmon_condition} to an incidence angle of $\sim39^{\circ}$, which is within the acceptance range of our experimental setup (35-75$^{\circ}$). %TODO point to Togawa section
An SEM image of one such region is shown in \ref{fig:fib-si-sem}.
